On exponential sums arising from the classical doubling method

### 2025-04-03 main.tex
wrote out details in proof of main theorem

\usepackage{amsmath, amsthm, amssymb}
\usepackage{enumerate}
\tolerance=500
\setlength{\emergencystretch}{3em}
\usepackage[margin=1.0in]{geometry}
\usepackage{xcolor}
\definecolor{cite}{rgb}{0.30,0.60,1.00}
\definecolor{url}{rgb}{0.00,0.00,0.80}
\definecolor{link}{rgb}{0.40,0.10,0.20}
\usepackage[pdfusetitle,colorlinks,linkcolor=link,urlcolor=url,citecolor=cite,pagebackref,breaklinks]{hyperref}
\usepackage{graphicx}
\usepackage{cleveref}
\usepackage{mathdots}
\usepackage{tikz-cd}
\usepackage{comment}
\usepackage{xypic}
\usepackage{mathtools}

@@

\begin{document}

@@

Given a torus $T \subset \GL_n\left(\finiteField\right)$ of the form $T \cong \multiplicativegroup{\finiteFieldExtension{\lambda}}$ where $\lambda \vdash n$ is a partition and given characters $\alpha \colon \multiplicativegroup{\finiteFieldExtension{\lambda}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon T \to \multiplicativegroup{\cComplex}$, we define $$\GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter} = \left(-1\right)^{\lengthof\left(\lambda\right)} q^{-\frac{n}{2}} \sum_{t \in T} \alpha^{-1}\left(t\right) \chi^{-1}\left(\det t\right) \fieldCharacter\left(\trace t\right).$$
Notice that if $\alpha = \alpha_1 \times \dots \times \alpha_{\lengthof\left(\lambda\right)}$, where $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{\lambda_j}} \to \multiplicativegroup{\cComplex}$ is a character for every $j$, then
$$\GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter} = \prod_{j=1}^{\lengthof\left(\lambda\right)} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\lambda_j}}.$$

@@

\subsection{Multiplicativity}
The goal of this section is to understand how the doubling method Jacobi sums behave under parabolic induction.

@@

We recall\[
	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n} = \prod_{a \in \mathbb{Z}/m\mathbb{Z}} \left(\algebraicGroup{\GL}_n\right)_a
\]
with Frobenius root action $$\Frobenius(g_0,g_1, \hdots, g_{m-1}) = (\Frobenius(g_{m-1}), \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{m-2})).$$

@@

Given a rational maximal torus $\algebraicGroup{T} \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$, a character of $\algebraicGroup{T}(\mathbb{F})$, and a non-trivial additive character $\psi$ of $\finiteFieldExtension{m}$, we define a Guass sum
\[
	\tau_{\algebraicGroup{T}}(\theta,\psi) := \varepsilon_{\algebraicGroup{
    \algebraicGroup{T}}}\sum_{t\in \tilde{\algebraicGroup{T}}^{\Frobenius}} \theta^{-1}(t)\psi(\trace(t)).
\]
\calvin{maybe should do inverses in the definition. Not sure if $\tau$ or $g$ make more sense.}

Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ and a Frobenius stable maximal tori $\algebraicGroup{T}^* \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ such that $\rho(\algebraicGroup{T}_0^*) \subseteq \algebraicGroup{T}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$. Define
\[
    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \tau_{\Tilde{\algebraicGroup{T}}}(\tilde{\theta} \times \chi(\det(t_0)),\psi).
\]
where $\chi$ is a multiplicative character of $\finiteFieldExtension{m}$ and $\psi$ and additive character of $\finiteFieldExtension{m}$.
The following lemma shows that this is well defined.

\begin{lemma}
\label{lemma:gl_invariance}
\begin{enumerate}[(i)]
	\item \label{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined} In the case $\rho$ is the identity, $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi)$ depends only on the semisimple conjugacy class of $(s_{\algebraicGroup{T},\theta})$ and the character $\chi$.
	\item $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi)$ is well defined i.e. independent of choice of $\algebraicGroup{T}_0$, $\algebraicGroup{T}^*$ and conjugacy class representative $w$.
\end{enumerate}
\end{lemma}
\begin{proof}
\begin{enumerate}[(i)]
	\item In this case when $T = \prod_{i} \multiplicativegroup{\finiteFieldExtension{n_i}}$ and $\theta = \prod_{i} \alpha_i$, we recover the Gauss sum
	\[
	g_{T,\rho}(\chi,\theta,\psi)  = \prod_i \tau(\alpha_i \times \chi, \fieldCharacter_{n_i}) = (-1)^nq^{-n/2}G(\tau \times \chi,\psi)
	\]
	where $\tau$ is any subrepresentation of $R_{T,\theta}$. By \Cref{thm:KondoClassical}, this only depends on geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$.
	\item For a Frobenius stable semisimple conjugacy class $(s)$ in $\GL_n$, we define
	\[
	g_{(s)}(\psi,\chi) := g_{T,\rho}(\chi,\theta,\psi) \textnormal{ for some } (T,\theta) \textnormal{ such that } (s_{T,\theta}) = (s)
	\]
	By (\ref{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined}) this is well defined. Then
	\[
	g_{T,\rho}(\chi,\theta,\psi)  = g_{(\rho(s_{T,\theta}))}(\psi,\chi)
	\]
	which is independent of of choice of $\algebraicGroup{T}^* \subset G^*$ and $\algebraicGroup{T} \subset \GL_n$.
\end{enumerate}
\end{proof}

@@

The proof strategy is to prove the following inductive statements
\begin{enumerate}[(A)]
	\item If for all representations with $\dim_{\mathbb{E}} V < n$, \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds, then \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non cuspidal representations with $\dim_{\mathbb{E}} V = n$.
	\item If \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non cuspidal representations with $\dim_{\mathbb{E}} V = n$, then it holds for all cuspidal representations with $\dim_{\mathbb{E}} V = n$.
\end{enumerate}
The key input to (A) is the multiplicativity [CITE] of the $\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter}$ factor. The key input to (B) is \Cref{lem:indep_geo_conj} along with results of Lusztig controlling the cupsidal elements in a Lusztig series.

\subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}}
We first reduce \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} to the case $G$ has connected center. For any irreducible representation $\pi$ of $G$ which is the a component of an irreducible representation $\tilde{\pi}$ of $\GroupExtension{G}$ restricted to $\pi$,
\[
    \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\tilde{\pi}}{\chi}{\fieldCharacter}.
\]

The following proposition implies that if $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$ then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{G}}{\tilde{s}}$ for $\tilde{s}$ only depending on $s$. Thus \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $G$ follows from \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $\GroupExtension{G}$ (see section 3.2).

@@

Our proof will be via induction as descriped in \ref{subsec:stability}.
%First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for all Levi factors. \\
\begin{proof}[Proof of (A)]
\calvin{should be short proof. Might not even need to put--just need to say both are multiplicative}
\end{proof}
\begin{proof}[Proof of (B)]

%Combining this with our inductive hypothesis implies \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for non cupsidal $\pi$.
By \Cref{lem:indep_geo_conj}, we know that for $R_T(\theta) = \sum c_{\pi} \pi$, 
$$\sum c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right).$$Subtracting our the equality for non-cupsidal $\pi$ we are left with:
$$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.

>>>>

\usepackage{amsmath, amsthm, amssymb}
\usepackage{enumerate}
\tolerance=500
\setlength{\emergencystretch}{3em}
\usepackage[margin=1.0in]{geometry}
\usepackage{xcolor}
\definecolor{cite}{rgb}{0.30,0.60,1.00}
\definecolor{url}{rgb}{0.00,0.00,0.80}
\definecolor{link}{rgb}{0.40,0.10,0.20}
\usepackage[pdfusetitle,colorlinks,linkcolor=link,urlcolor=url,citecolor=cite,pagebackref,breaklinks]{hyperref}
\usepackage{graphicx}
\usepackage{cleveref}
\usepackage{mathdots}
\usepackage{tikz-cd}
\usepackage{comment}
\usepackage{xypic}
\usepackage{mathtools}
%\usepackage{xcolor}

@@

\begin{document}
%\pagecolor{black}
%\color{white}

@@

Given a torus $T \subset \GL_n\left(\finiteField\right)$ of the form $T \cong \multiplicativegroup{\finiteFieldExtension{\lambda}}$ where $\lambda \vdash n$ is a partition and given characters $\alpha \colon \multiplicativegroup{\finiteFieldExtension{\lambda}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon T \to \multiplicativegroup{\cComplex}$, we define $$\GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter} = \left(-1\right)^{\lengthof\left(\lambda\right)} q^{-\frac{n}{2}} \sum_{t \in T} \alpha^{-1}\left(t\right) \chi^{-1}\left(\det t\right) \fieldCharacter\left(\trace t\right).$$
We also define $$\GaussSumSingleTorusCharacter{T}{\alpha}{\fieldCharacter} = \GaussSumTorusCharacter{T}{\alpha}{1}{\fieldCharacter}.$$
Notice that if $\alpha = \alpha_1 \times \dots \times \alpha_{\lengthof\left(\lambda\right)}$, where $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{\lambda_j}} \to \multiplicativegroup{\cComplex}$ is a character for every $j$, then
\begin{align}
	\label{eq:Gauss_multiplicitive}
	\GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter} = \prod_{j=1}^{\lengthof\left(\lambda\right)} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\lambda_j}}.
\end{align}

@@

\subsection{Multiplicativity}\label{subsec:multiplicativity}
The goal of this section is to understand how the doubling method Jacobi sums behave under parabolic induction.

@@

We recall\[
	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n} = \prod_{a \in \mathbb{Z}/m\mathbb{Z}} \left(\algebraicGroup{\GL}_n\right)_a
\]
with Frobenius root action $$\Frobenius(g_0,g_1, \hdots, g_{m-1}) = (\Frobenius(g_{m-1}), \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{m-2})).$$ Thus we identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}(\finiteField) = \algebraicGroup{\GL}_n(\finiteFieldExtension{m})$ via the first coordinate $g_0$.

@@

%Given a rational maximal torus $\algebraicGroup{T} \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$, a character of $\algebraicGroup{T}(\mathbb{F})$, and a non-trivial additive character $\psi$ of $\finiteFieldExtension{m}$, we define a Guass sum
%\[
%	\tau_{\algebraicGroup{T}}(\theta,\psi) := \varepsilon_{\algebraicGroup{
%    \algebraicGroup{T}}}\sum_{t\in \tilde{\algebraicGroup{T}}^{\Frobenius}} \theta^{-1}(t)\psi(\trace(t)).
%\]
%\calvin{maybe should do inverses in the definition. Not sure if $\tau$ or $g$ make more sense.}

Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ and a Frobenius stable maximal tori $\algebraicGroup{T}^* \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ such that $\rho(\algebraicGroup{T}_0^*) \subseteq \algebraicGroup{T}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$. Define
\[
    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \tau_{\Tilde{\algebraicGroup{T}}}(\tilde{\theta} \times \chi \circ \det,\psi) = q^{-(nm)/2}\epsilon_{\Tilde{\algebraicGroup{T}}}\sum_{t \in \tilde{\algebraicGroup{T}}^{\Frobenius}} \tilde{\theta}^{-1}(t)\chi^{-1}(\det(t)) \psi(\trace(t)).
\]
\calvin{should the power be $q^{(-nm)/2}$ or $q^{-n/2}$?}
Here $\chi \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ and $\fieldCharacter \colon \finiteFieldExtension{m} \to \multiplicativegroup{\cComplex}$ are characters and $\chi_0 \circ \det \colon \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}\left(\finiteField\right) \to \multiplicativegroup{\cComplex}$ is given by $$\left(\chi \circ \det\right)\left(g_0,\dots,g_{m-1}\right) = \chi\left(\det g_0\right)$$ \elad{This is weird. Maybe we should just say that we identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}\left(\finiteField\right) = \GL_n\left(\finiteFieldExtension{m}\right)$ by $\left(g_0,\dots,g_{m-1}\right) \mapsto g_0$?}\calvin{yeah that makes sense}.
The following lemma shows that this is well defined.

\begin{lemma}
\label{lemma:gl_invariance}
\begin{enumerate}[(i)]
	\item \label{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined} In the case $\rho$ is the identity, $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi)$ depends only on the semisimple conjugacy class of $(s_{\algebraicGroup{T},\theta})$ and the character $\chi$.
	\item $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi)$ is well defined i.e. independent of choice of $\algebraicGroup{T}_0$, $\algebraicGroup{T}^*$ and conjugacy class representative $w$.
\end{enumerate}
\end{lemma}
\begin{proof}
\begin{enumerate}[(i)]
	\item In this case when $T \cong \multiplicativegroup{\finiteFieldExtension{\lambda}}$, we recover the Gauss sum
	\[
	g_{T,\rho}(\chi,\theta,\psi) = \GaussSumTorusCharacter{T}{\theta}{\chi}{\fieldCharacter} = \left(-1\right)^n \GaussSumScalar{\tau \times \chi}{\fieldCharacter},
	\]
	where $\tau$ is any subrepresentation of $R_{T,\theta}$. By \Cref{thm:KondoClassical}, this only depends on geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$.
	\item For a Frobenius stable semisimple conjugacy class $(s)$ in $\GL_n$, we define
	\[
	g_{(s)}(\psi,\chi) := g_{T,\rho}(\chi,\theta,\psi) \textnormal{ for some } (T,\theta) \textnormal{ such that } (s_{T,\theta}) = (s)
	\]
	By (\ref{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined}) this is well defined. Then
	\[
	g_{T,\rho}(\chi,\theta,\psi)  = g_{(\rho(s_{T,\theta}))}(\psi,\chi)
	\]
	which is independent of of choice of $\algebraicGroup{T}^* \subset G^*$ and $\algebraicGroup{T} \subset \GL_n$.
\end{enumerate}
\end{proof}

@@

The proof strategy is to prove the following inductive statements
\begin{enumerate}[(A)]
	\item If for all representations with $\dim_{\mathbb{E}} V < n$, \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds, then \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non cuspidal representations with $\dim_{\mathbb{E}} V = n$.
	\item If \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non cuspidal representations with $\dim_{\mathbb{E}} V = n$, then it holds for all cuspidal representations with $\dim_{\mathbb{E}} V = n$.
\end{enumerate}
The key input to (A) is the multiplicativity of the $\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter}$ factor. The key input to (B) \Cref{lem:indep_geo_conj} along with results of Lusztig controlling the cupsidal elements in a Lusztig series.

\subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}}
We first reduce \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} to the case $G$ has connected center. For any irreducible representation $\pi$ of $G$ which is subrepresentation of an irreducible representation $\tilde{\pi}$ of $\GroupExtension{G}$ restricted to $\pi$,
\[
    \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\tilde{\pi}}{\chi}{\fieldCharacter}.
\]

Since the map $\algebraicGroup{\GroupExtension{G}}^*(\finiteField) \to \algebraicGroup{G}^*(\finiteField)$ is surjective \calvin{check this!}, the following proposition implies that there exists $\tilde{s}$ depending on $s$ such that each $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$ is an irreducible subrepresentation of some $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ restricted to $G$. Thus \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $G$ follows from \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $\GroupExtension{G}$.

@@

Our proof will be via induction as described in \ref{subsec:stability}.
%First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for all Levi factors. \\
\begin{proof}[Proof of (A)]
	Since every proper parabolic of $H$ is contained in a proper parabolic of the form $\algebraicGroup{\GL}_n \times H'$ where $H'$ is as in \Cref{subsec:multiplicativity}, the multiplicativity of the left hand side of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} follows from \Cref{thm:multiplicativity-in-terms-of-gamma-factors}. \\
	For the right hand side, first the following result of Lusztig tells us that if $\pi \in \LusztigSeries{
		\algebraicGroup{G}^{\Frobenius}}{(s)}$ is contained in the parabolical induction of $\sigma$ from a Levi $L$, then $\sigma \in \LusztigSeries{
		\algebraicGroup{L}^{\Frobenius}}{(s)}$.
		\begin{proposition}[{\cite[Proof of Corollary 3.3.21]{GeckMalle2020}}]
			For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(\FrobeniusFixedPoints{\algebraicGroup{P}},\sigma\right)$ where $\algebraicGroup{P}$ is a parabolic subgroup of $\algebraicGroup{\GroupExtension{G}}$ with Levi part $\algebraicGroup{L}$ with $s \in \DualFrobeniusFixedPoints{L}$ and $\sigma \in \LusztigSeries{\FrobeniusFixedPoints{L}}{s}$ is an irreducible cuspidal representation.
		\end{proposition}
	Thus if $\pi$ is contained in the parabolical induction from a proper Levi $L$ then $(T,\theta)$ is geometrically conjugate to $(T_1 \times T_2,\theta_1 \times \theta_2)$ for $T_1 \times T_2$ a torus of $L$. As proved in \Cref{lem:indep_geo_conj}, $$g_{T \cap G}(\chi,\theta|_{T \cap G},\psi) = g_{(T_1 \times T_2) \cap G}(\chi,\left(\theta_1\times \theta_2\right)|_{(T_1 \times T_2) \cap G},\psi).$$ The right hand of the above is multiplicative since Gauss sums are multiplicative by \Cref{eq:Gauss_multiplicitive}.
\end{proof}
\begin{proof}[Proof of (B)]
%Combining this with our inductive hypothesis implies \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for non cupsidal $\pi$.
By \Cref{lem:indep_geo_conj}, we know that for $R_T(\theta) = \sum c_{\pi} \pi$, 
$$\sum c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right).$$Subtracting our the equality for non-cupsidal $\pi$ we are left with:
$$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.
